A simulation framework for exploring spatio-temporal dynamics in mixed fisheries

### 2018-01-19 write_up/mixfishsim_ecolmod.tex
Manuscript edits

We developed a simulation model with a modular discrete-event approach to each
of the processes so that they can occur on different time-scales. The fishing
model operated on a tow-by-tow basis, while population dynamics (fishing and
natural mortality, growth) operate on a daily time-step.  Population movement
occurs on a two-weekly time-step, while recruitment occurs periodcally each
year for a set time period (e.g. 3 weeks) at at specified point individual to a
species. The model structure is summerised in Figure 1.  \\

>>>>

We developed a simulation model with a modular discrete event-based approach to
each of the processes so that they can occur on independent time-scales
suitable for the processes. The fishing model operated on a tow-by-tow basis,
while population dynamics (fishing and natural mortality, growth) operate on a
daily time-step.  Population movement occurs on a two-weekly time-step, while
recruitment occurs periodcally each year for a set time period (e.g. 3 weeks)
at at specified point individual to a species. The model structure is
summerised in Figure 1.  \\

In the following section, we describe each of the model components; 1)
Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
fishery dynamics. \\
